---
title: "Assignment-4"
author: "Saurabh Patloori"
date: "2023-10-29"
output:
  pdf_document: default
  html_document: default
---
```{r}
Pharmaceuticals <- read.csv("C:/Users/patlo/OneDrive/Desktop/Pharmaceuticals.csv")
```

```{r}
library(tidyverse)# For Data manipulation

```

```{r}
library(factoextra)# Used for clustering algorithms and visualization

```

```{r}
library(dplyr)
library(ggplot2)
library(cluster)

```

```{r}
Pharma_data <- na.omit(Pharmaceuticals) 
#Provides the data after removing the incomplete cases.
Pharma_data


```

```{r}
#Taking the quantitative variables(1-9) to cluster the 21 firms
row.names(Pharma_data)<- Pharma_data[,1]
Pharma_data1<- Pharma_data[,3:11]
# Considering only numercial values i.e., 3-11 columns from csv file
head(Pharma_data1)

```
```{r}
#Normalizing the data frame with scale method
Pharma_data2<-scale(Pharma_data1)
head(Pharma_data2)
```
```{r}
#To determine the number of clusters to do the cluster analysis using Elbow Method
fviz_nbclust(Pharma_data2, kmeans, method = "wss")

```

```{r}
##By seeing the above graph from Elbow method, Graph is not 
#clear to choose k=2 or 3 or 4 or 5.
#Silhouette method for determining no of clusters


fviz_nbclust(Pharma_data2, kmeans, method = "silhouette")

```

```{r}
#Applying K-means
set.seed(64060)
k_5<- kmeans(Pharma_data2,centers=5,nstart = 25)

```

```{r}
#Visualizing the output
#centroids
k_5$centers

```
```{r}
fviz_cluster(k_5,data = Pharma_data2) # to Visualize the clusters

```

```{r}
k_5

```

```{r}

distance<- dist(Pharma_data2, method = "euclidean")
fviz_dist(distance)

```

```{r}
## I can see there are 5 clusters and the center is defined after 25 restarts
#which is determined in kmeans.
#K - Means Cluster Analysis- Fit the data with 5 clusters
fit<-kmeans(Pharma_data2,5)

```


```{r}
#Finding the mean value of all quantitative variables for each cluster
aggregate(Pharma_data2,by=list(fit$cluster),FUN=mean)

```

```{r}

##To view the cluster plot

clusplot(Pharma_data2,fit$cluster,color =
           TRUE,shade = TRUE,labels = 2,lines = 0)

```

#Task 2: Analyze the clusters in relation to the numerical variables used in their creation.
AGN, PHA, and BAY are in #Cluster_1, and they have the highest PE_Ratio. #By looking at each cluster's mean values for every quantitative variable. The ROE percentage is low.
The companies in #Cluster_2 with the largest market capitalization and good leverage values are #JNJ, MRK, GSK, and PFE.
The three stocks in #Cluster_3 with the lowest beta and asset turnover are #AHM, AVE, and WPI.
Task 3: Are there any patterns among the clusters concerning the numerical variables (10–12)?
*(those not used in the formation of clusters)
#Because cluster 1 has the highest PE Ratio, it should be held in compliance with media recommendations.
#For cluster 2: It has the biggest market capitalization and a good leverage value. Besides, they can be pretty aggressive.#In cluster 3, the lowest asset turnover and beta are observed. Nonetheless, positive media endorsements predominate.#For cluster 4: Considering the high leverage ratio, they have a cautious recommendation.
#Cluster 5: They have the lowest revenue growth, the highest asset turnover, and the biggest net profit margin.


#Task 4: Give each cluster a fitting name using some or all of the variables in the dataset.
#Cluster 1: Hold cluster; they have respectable numbers.
#4 Group 2: Light Buy or Hold a Cluster.
#Cluster 3: Buying or Selling
#Cluster 4: Buy Cluster—it is comparatively stable.








